Structured Versus Decorated Cospans

### 2020-12-29 cospans.tex
small edits

The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem related to the existence of colimits as well as left adjoints for opfibrations. We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem. The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.

@@

Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold and thus the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}

>>>>

The ``corresponding pseudofunctor'' comes from the so-called monoidal Grothendieck construction, and the conditions of this theorem relate to the existence of colimits as well as left adjoints for opfibrations. We first sketch the relevant underlying framework in detail, and then we proceed to the proof of the theorem. The basics of fibration theory needed for our purposes are recalled in \cref{sec:fibrations}.

@@

Finally, the rest of the axioms of \cref{defn:monoidal_double_functor} hold: on the cospan level they are easy to verify, whereas on the decoration level they entail non-trivial calculations involving universal property arguments. In conclusion, the double isomorphism \cref{eq:doubleiso} is an isomorphism of symmetric monoidal double categories. 
\end{proof}
